CDSR Human Data/Modelling Paper

### 2013-09-11 scenarios/cdsr/trunk/papers/ACS2013/main.tex
JK updated the text and removed table 3

As noted above, we controlled for left-right bias by flipping some of the stimuli on the horizontal axis. These flipped stimuli included the classroom stimuli (c), (e) and (f). This flipping of stimuli gave us the opportunity to compare the results of the sweetspots rankings between this pairs of stimuli trials. Given the horizontal flipping of the stimuli it was expected that the sweetspot for the stimuli should also be flipped between P1 and P3. To test whether or not the expected shift in the sweetspots occurred we ran two-tailed two sample t-tests between the sweetspots of the flipped and non-flipped stimuli pairs. %Table \ref{tab:flipped-point-likert-scores} lists the results of this trial. 
In all cases the results indicated that there was not enough evidence to reject the null hypothesis, in other words there was no statistical difference between the rating of the sweetspot for the non-flipped stimuli and the rating of the sweetspot for the flipped stimuli. In other words, the sweetspot flipped from P1 to P3 systematically with the horizontal flipping of the stimuli.

@@

\begin{table}
\centerline{
\begin{tabular}{c c c c }
\hline
Domain & \multicolumn{3}{c}{Classrom/Front of Room} \\
$H_0$ & $H_A$ & $\alpha$ & p-value\\
$\mu(c.P1)=\mu(c-flipped.P3)$ & $\mu(c.P1)!=\mu(c-flipped.P3)$ & $0.05$ & $0.6315$\\
$\mu(e.P1)=\mu(e-flipped.P3)$ & $\mu(e.P1)!=\mu(e-flipped.P3)$ & $0.05$ & $0.7358$\\
$\mu(f.P1)=\mu(f-flipped.P3)$ & $\mu(f.P1)!=\mu(f-flipped.P3)$ & $0.05$ & $0.2592$\\
\hline
\hline
\end{tabular}
}
\label{tab:flipped-point-likert-scores}
\caption{Two Tailed Two Sample T-Tests for flipped stimuli pair trials.}
\end{table}

>>>>

As noted above, we controlled for left-right bias by flipping some of the stimuli on the horizontal axis. These flipped stimuli included the classroom stimuli (c), (e) and (f). This flipping of stimuli gave us the opportunity to compare the results of the sweetspots rankings between this pairs of stimuli trials. Given the horizontal flipping of the stimuli it was expected that the sweetspot for the stimuli should also be flipped between P1 and P3. To test whether or not the expected shift in the sweetspots occurred we ran two-tailed two sample t-tests between the sweetspots of the flipped and non-flipped stimuli pairs. In all cases the results indicated that there was no statistical difference between the rating of the sweetspot for the non-flipped stimuli and the rating of the sweetspot for the flipped stimuli. In other words, the sweetspot flipped from P1 to P3 systematically with the horizontal flipping of the stimuli.

@@

%\begin{table}
%\centerline{
%\begin{tabular}{c c c c }
%\hline
%Domain & \multicolumn{3}{c}{Classrom/Front of Room} \\
%$H_0$ & $H_A$ & $\alpha$ & p-value\\
%$\mu(c.P1)=\mu(c-flipped.P3)$ & $\mu(c.P1)!=\mu(c-flipped.P3)$ & $0.05$ & $0.6315$\\
%$\mu(e.P1)=\mu(e-flipped.P3)$ & $\mu(e.P1)!=\mu(e-flipped.P3)$ & $0.05$ & $0.7358$\\
%$\mu(f.P1)=\mu(f-flipped.P3)$ & $\mu(f.P1)!=\mu(f-flipped.P3)$ & $0.05$ & $0.2592$\\
%\hline
%\hline
%\end{tabular}
%}
%\label{tab:flipped-point-likert-scores}
%\caption{Two Tailed Two Sample T-Tests for flipped stimuli pair trials.}
%\end{table}
